\section{Introduction}\label{}
    %Modeling and simulation codes will play a critical role in licensing
    %advanced nuclear reactors. In preparation for advanced nuclear technology,
    %both the \Gls{doene} and the \Gls{nrc} identified several technical gaps in
    %current \Gls{mns} tools that are necessary for efficient and effective
    %license application reviews \citep{betzler_modeling_2019,
    %usnrc_nonlwr_2020-1}. Both \Gls{doene} and the \Gls{nrc} have specifically
    %identified depletion to be a key modeling feature for advanced nuclear
    %reactors.

    Accurate simulations of advanced reactors on exascale computing hardware
    requires state-of-the-art software tools in Monte Carlo transport and
    heat-coupled computational fluid dynamics
    ~\citep{romano2021nse,merzari2023sc}.  These methods are computationally
    expensive, but deliver high confidence in their results. If any component in
    this tool chain could be simplified or sped up, it would reduce the
    computational cost on and economic cost from these exascale machines. For
    Monte Carlo neutron transport, depletion simulations are one of the more
    expensive simulations. {\it Depletion} is the process by which the nuclide
    composition changes due to nuclear transmutation and decay reactions
    occurring in a material subject to irradiation. Depletion capabilities were
    recently added \citep{ romano_depletion_2021} to OpenMC
    \citep{romano_openmc_2015}, an open source, community developed Monte Carlo
    particle transport code. The depletion solver utilizes OpenMC's Python API
    to iteratively run a transport simulation, calculate transmuation reaction
    rates, solve the depletion matrix (Eq. \ref{eq:depletion-matrix-t}), and
    update the material composition. This makes transport-coupled depletion
    calculations computationally expensive, expecially for large reactor models.
    
    In the present work, we describe a new method for running depletion
    calculations without the need to iteratively run transport calculations by
    using pre-calculated microscopic cross sections and fluxes for each depletion
    step. At most, only one transport calculation needs to be run to generate
    these cross sections and fluxes. Neutron transport and depletion are tightly
    coupled because the change in material composition can result in changes to
    the spatial distribution of reaction rates. If few materials are used in a
    transport-independent depletion calculation, this effectively removes
    spatial effects of the changing material composition due to the static
    fluxes and cross sections.

    This limits the practical application of transport-independent depletion to
    domains where capturing spatial effects are a secondary concern. One
    such application is in global fuel-cycle analysis where we are more
    concerned with the overall change in material composition. Fuel cycle
    simulations typically model many different reactors simultaneously over
    long time periods. The capabilities described in this paper
    have been utilized in Cyclus \citep{huff_fundamental_2016} -- an open source
    fuel cycle simulator -- for coupling depletion to the fuel cycle
    simulaton \citep{bachmann_os_2024}. Another area of application is in
    facilities where the coupling between neutron transport and depletion is
    effectively one-way.  This is often the case for experimental facilities
    with a neutron source where the source rate is high enough to cause
    activation of materials but not high enough to produce meaningful burnup of
    materials. Many proposed fusion energy facilities would fall into this
    category. For such applications, it is unnecessary to run a fully coupled
    simulation between neutron transport and depletion; instead, a neutron
    transport simulation corresponding to the beginning of irradiation can
    determine reaction rates relative to the neutron source rate, and then the
    depletion calculation can be performed using the reaction rates scaled by
    any changes in the neutron source rate over time. For fusion systems, these
    calculations are often carried out with FISPACT-II~\citep{sublet2017nds};
    See \citet{eade2020nf} for a recent example. The capabilities described in
    this paper have also been utilized for a recent study of shutdown dose rate
    in fusion systems~\citep{peterson2024nf}.

    This paper is organized as follows: In Section \ref{sec:methods}, we describe
    the methods and algorithms used to calculate reaction rates using the new
    depletion capabilities. In Section \ref{sec:results}, we describe our
    simulation and analyze the results. In Section \ref{sec:conclusion}, we
    summarize our results, and discuss some gaps in the current implementation
    of the new feature.


